---
title: "Mapping the Evolution of the Digital Divide: Comparative Analysis of European Research and the Multifaceted Dimensions in Italian Enterprises"
author: "Luis Carlos Castillo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  beamer_presentation:
    keep_tex: yes
    citation_package: natbib
    includes:
      in_header: mystyle2.tex
institute: |
  | Binational Doctorate
  | University of Urbino and Universty of Bremen
  | Ph.D. Program in Global Studies
  | Supervisor: Prof. Francesco Vidoli
  | Co-Supervisor: Prof. Dr. Christian Cordes
editor_options:
  markdown:
    wrap: 72
link-citations: yes
linkcolor: myblue
natbiboptions: round
header-includes:
 - \usepackage{etoolbox}
 - \AtBeginEnvironment{thebibliography}{\scriptsize}
bibliography: ShiftPatterns.bib
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F )
kableExtra.auto_format = FALSE
knitr.table.format = "latex"
knitr::opts_knit$set(kable.force.latex = TRUE)

```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r Loading packages, include=FALSE}
library(tidyverse)
library(devtools)
library(here)
library(bibliometrix)
library(stringr)
library(readr)
library(visdat)
library(stringr)
library(dplyr)
library(readxl)
library(janitor)
library(ggplot2)
library(gridExtra)
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
library(rmarkdown)
library(tidytext)
library(knitr)
library(qwraps2)
library(dplyr)
library(tables)
library(bibtex)
library(igraph)
library(RColorBrewer)
library(Matrix)
library(flextable)
library(ggpubr)
library(cowplot)
library(ggeasy)
library(Hmisc)
library(gridGraphics)
library(gridBase)
library(tinytex)
library(stargazer)

```

# Cumulative Dissertation

```{=tex}
\begin{center}
\includegraphics[width=1\textwidth, height=0.75\textheight]{structure_thesis.png}
\end{center}
```
# Chapter 3

## \centering{Exploring Patterns and Shifts: Factor Analysis of the First  and Second-Level Digital Divide in Italian Enterprises}

# Content I

1.  Introduction

2.  Digital divide overview

3.  Objectives and Research Questions

4.  Theoretical Framework

5.  Data

6.  Methodology

7.  Results

# 1. Introduction

-   DT play a pivotal role in reshaping business models [@trischler2023]
    , driving innovation [@ciarli2021], and fostering competitive
    advantages [@jeganjosephjerome2024].

-   The unequal adoption of DT has led to significant challenge: the
    digital divide.

-   The digital divide at the firm level is a multifaceted gap
    characterized not only by disparities in access, skills and usage of
    DT, but also the derived benefits from different types of use.

-   While the digital divide is a global issue, its impact on
    enterprises, especially in Italy, presents unique challenges and
    opportunities.

# 2. Digital divide overview

-   The digital divide at the firm level is a topic that needs further
    exploration [@pejicbach2013; @acilar2021; @lythreatis2022;
    @thonipara2023; @shakina2021a; @siqueira2019].

-   **Fragmented research:** Highlights the different frameworks and
    measurements in the field. [@forman2002; @vehovar2006;
    @shakina2021a; @acilar2021; @ndulu2022].

-   **Impact on Business Performance:** Addresses how DT impact
    innovation [@usai2021], productivity [@cusolito2020], and wages
    between high and low skilled labor [@vasilescu2020] . Leaving room
    for further analysis on the underlying causes of digital
    disparities.

# 3. Objectives

-   Develop composite indices to track trends in the first and
    second-level digital divide.

-   Analyze variations in the first and second-level digital divide
    across firm sizes, sectors, and regions in Italy.

-   Evaluate the alignment of resources and technology integration
    theory with observed data.

-   Propose targeted policy interventions based on research findings.

# 3.1. Research Questions

-   How does the Resources and Technology Integration theory reflect
    observed patterns in DT adoption across different Italian enterprises?

-   What are the evolving patterns and shifts in access, skills, and usage
    among Italian enterprises, and how do these dynamics reflect the
    disparities between the three indices across different firm sizes,
    sectors, and regions over a six-year period?

-   According to the findings, what policy interventions can be
    recommended to help Italian enterprises more effectively bridge the
    digital divide?

# 4. Theoretical Framework

-   Adaptation of the Resources and Appropriation Theory (van Dijk 2005,
    2020) toward the Resources and Technology Integration Theory.

```{=tex}
\begin{center}
\includegraphics[width=1\textwidth, height=0.75\textheight]{dd_model.png}
\end{center}
```

# 5. Data

```{r avgYear, echo=FALSE}

load(here("Data", "Processed", "CI_clean.rda"))

# Calculate the number of observations per year
options(scipen=999)
observations_per_year <- CI_clean %>%
  group_by(year) %>%
  summarise(count = n())

avgPerYear <- round(mean(observations_per_year$count),2)

```

-   The dataset was derived from the ICT Usage in Enterprises Survey
    conducted annually between 2014 and 2019 by ISTAT.

-   Each year, the survey collected an average of `r avgPerYear`
    observations.

-   The analysis focused on a selection of variables from the survey
    that met certain criteria.

-   Considerations and Limitations.

    -   Independence of Annual Data
    
-    Data treatments, codes, and summary statistics are available on my [GitHub repository](https://github.com/luchocastillo84/Factor_Analysis_Digital_Divide/tree/main) for replicability and further analysis.

# 5.1 List of Variables I

-   In total 26 variables were used.

    -   Access index 6 variables
    -   Skills index 9 variables
    -   Usage index 11 variables

```{=tex}
\begin{center} 
\includegraphics[width=1\textwidth]{access_vars.png}
\end{center}
```
-   

    (C) Continuous variables, (B) Binary variables.

# 5.2 List of Variables II

```{=tex}
\begin{center}
\includegraphics[width=1\textwidth,height=0.7\textheight]{skills_usage_vars.png}
\end{center}
```

# 6 Methodology

-   The indices were constructed using dimensionality reduction
    techniques Factor Analysis for Mixed Data (FAMD) and Multiple
    Correspondence Analysis (MCA).
-   Visualise and measure adoption patterns.

$$ \text{Access Index}_i = a_1 \cdot X1_i + a_2 \cdot X2_i + \ldots + a_6 \cdot X6_i $$
$$ \text{Skills Index}_i = b_1 \cdot Y1_i + b_2 \cdot Y2_i + \ldots + b_6 \cdot Y6_i $$
$$ \text{Usage Index}_i = c_1 \cdot Z1_i + c_2 \cdot Z2_i + \ldots + c_{11} \cdot Z11_i $$


Where $\mathbf{X}$, $\mathbf{Y}$, and $\mathbf{Z}$ are the matrices of observations, and $\mathbf{a}$, $\mathbf{b}$, and $\mathbf{c}$ are the vectors of weights derived from FAMD and MCA contributions of each variable to the retained dimensions.


# 7. Results I

```{r yearTrendSize, echo=FALSE}
load(here("Scripts", "Environments",  "ResultsRevBySizeWeighted.RData"))

line_plot_by_smeR

```

# 7. Key takeaways I


- While SMEs can maintain continuous growth in access, larger firms face different challenges.

- These findings align with Bratta et al. (2020), who discuss the hyper-depreciation measure issued in 2016.

- SMEs face more challenges in acquiring digital skills. There is a significant shortage of ICT graduates in Italy according to the “Digital Skills Observatory” in 2019.

- A higher usage index is present in SMEs as existing technologies need to be operated either by outsourcing digital skills or maximising the existing workforce.


# 7.1. Results II

```{r yearTrendMac, echo=FALSE}
load(here("Scripts", "Environments", "ResultsRevBySizeWeighted.RData"))

line_plot_by_mac

```

# 7.1. Key takeaways II

- Notable progress in digital access across sectors due to effective policy measures like hyper-depreciation.

- The digital skills index remains low, highlighting challenges in developing necessary competencies.

- Commercial, Industrial, Service Sectors: Growing digital access and stable usage, but significant skills gap.

- Creative Industries and ICT Sector: High levels of access and skills but moderate usage, reflecting different technological needs in workflows.


# 7.2. Results III

```{r yearTrendReg, echo=FALSE}

load(here("Scripts", "Environments","ResultsRevBySizeWeighted.RData"))

line_plot_by_region

```

# 7.2. Key takeaways III

- Northern and Central Regions:

    - Significant improvements in digital access.
    - Benefits from robust industrial bases and policy interventions.
    - Persistent skills gap, slight increase towards the end.
    
- South and Insular Regions:

    - Lag behind in both access and skills. Reflecting systemic issues.
    - Need targeted policy efforts.
    
- Usage Trends:

    - Similar trends across regions.
    - DT integration driven by national policies, market forces, and sectoral requirements.
    
    
    

# 7..3 Evaluating Theory in Light of Data

Sequential Model Challenges: While the theory posits a sequential model
of technology adoption (access → skills → usage), our data shows that
skills development has not kept pace with access, and usage sometimes
surpasses skills. This indicates that firms may adopt technologies
without fully developing digital skills, relying on external support or
simpler applications.

Inequality in Resources: The theory suggests inequality in
access to resources leads to disparities in technology adoption.
However, our data only infers this inequality without direct proof.

# 7.4. Key Interventions

Accelerate Digital Skills Acquisition: Promote and subsidize e-learning
platforms and certification programs for rapid, flexible digital skills
training.

Enhance Digital Infrastructure and Support for SMEs in Lagging Regions:
Expand broadband and mobile network coverage in under-served regions
through public-private partnerships.

# 8. Q&A

Thank you for your attention

# References {.allowframebreaks}

::: {#refs}
:::
