---
title: 'Tracking the Digital Divide: Factor Analysis and Time Trends in Italian Firms'
author: "Luis Carlos Castillo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  beamer_presentation:
    keep_tex: yes
    citation_package: natbib
    includes:
      in_header: mystyle3.tex
institute: |
  | Binational Doctorate
  | University of Urbino and Universty of Bremen
  | Ph.D. Program in Global Studies
  | Supervisor: Prof. Francesco Vidoli
  | Co-Supervisor: Prof. Dr. Christian Cordes
editor_options:
  markdown:
    wrap: 72
link-citations: yes
linkcolor: myblue
natbiboptions: round
header-includes:
 - \usepackage{etoolbox}
 - \AtBeginEnvironment{thebibliography}{\scriptsize}
bibliography: ShiftPatterns.bib
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = F, message = F )
kableExtra.auto_format = FALSE
knitr.table.format = "latex"
knitr::opts_knit$set(kable.force.latex = TRUE)



```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r Loading packages, include=FALSE}
library(tidyverse)
library(devtools)
library(here)
library(bibliometrix)
library(stringr)
library(readr)
library(visdat)
library(stringr)
library(dplyr)
library(readxl)
library(janitor)
library(ggplot2)
library(gridExtra)
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
library(rmarkdown)
library(tidytext)
library(knitr)
library(qwraps2)
library(dplyr)
library(tables)
library(bibtex)
library(igraph)
library(RColorBrewer)
library(Matrix)
library(flextable)
library(ggpubr)
library(cowplot)
library(ggeasy)
library(Hmisc)
library(gridGraphics)
library(gridBase)
library(tinytex)
library(stargazer)

source(here("Scripts", "Functions", "create_summary_table.R"))
source(here("Scripts", "Functions", "yearly_stats_and_plot.R"))

## Scheme 11: year,  region, Revenue_K,  sec_name, size_rev

```

# Cumulative Dissertation

```{=tex}
\begin{center}
\includegraphics[width=1\textwidth, height=0.75\textheight]{structure_thesis.png}
\end{center}
```



# 1. Introduction

-   DT play a pivotal role in reshaping business models [@trischler2023]
    , driving innovation [@ciarli2021], and fostering competitive
    advantages [@jeganjosephjerome2024].

-   The unequal adoption of DT has led to significant challenge: the
    digital divide.

-   The digital divide at the firm level is a multifaceted gap
    characterized not only by disparities in access, skills and usage of
    DT, but also the derived benefits from different types of use.

-   While the digital divide is a global issue, its impact on
    enterprises, especially in Italy, presents unique challenges and
    opportunities.


# 2. Objectives

-   Develop composite indices to track trends in the first and
    second-level digital divide.

-   Analyze variations in the first and second-level digital divide
    across firm sizes, sectors, and regions in Italy.

-   Evaluate the alignment of resources and technology integration
    theory with observed data.

-   Propose targeted policy interventions based on research findings.

# 3.1. Research Questions

-   How does the Resources and Technology Integration theory reflect
    observed patterns in DT adoption across different Italian enterprises?

-   What are the evolving patterns and shifts in access, skills, and usage
    among Italian enterprises, and how do these dynamics reflect the
    disparities between the three indices across different firm sizes,
    sectors, and regions over a six-year period?

-   According to the findings, what policy interventions can be
    recommended to help Italian enterprises more effectively bridge the
    digital divide?


# 5. Data

```{r avgYear, echo=FALSE}

load(here("Data", "Processed", "CI_clean.rda"))

# Calculate the number of observations per year
options(scipen=999)
observations_per_year <- CI_clean %>%
  group_by(year) %>%
  summarise(count = n())

avgPerYear <- round(mean(observations_per_year$count),2)

```

-   The dataset was derived from the ICT Usage in Enterprises Survey
    conducted annually between 2014 and 2019 by ISTAT.
    
-   In total, 29 variables were used to extract three factors that represent the theoretical constructs.

    - Access index: 6 variables
    - Skills index: 9 variables
    - Usage index: 11 variables
    - **Control variable:** Firm size with three categories (small, medium, large)

-   Considerations and Limitations.

    -   Independence of Annual Data
    
-    Data treatments, codes, and summary statistics,  are available on my [GitHub repository](https://github.com/luchocastillo84/Factor_Analysis_Digital_Divide/tree/main) for replicability and further analysis.


# 6 Methodology

-   The indices were constructed using dimensionality reduction
    techniques Factor Analysis for Mixed Data (FAMD) and Multiple
    Correspondence Analysis (MCA).
-   Visualise and measure adoption patterns.


$$ \text{Access Index}_i = a_1 \cdot X1_i + a_2 \cdot X2_i + \ldots + a_6 \cdot X6_i + d \cdot \text{Size}_i $$
$$ \text{Skills Index}_i = b_1 \cdot Y1_i + b_2 \cdot Y2_i + \ldots + b_6 \cdot Y6_i + e \cdot \text{Size}_i $$
$$ \text{Usage Index}_i = c_1 \cdot Z1_i + c_2 \cdot Z2_i + \ldots + c_{11} \cdot Z11_i + f \cdot \text{Size}_i $$

Where $\mathbf{X}$, $\mathbf{Y}$, and $\mathbf{Z}$ are the matrices of observations, $\mathbf{a}$, $\mathbf{b}$, and $\mathbf{c}$ are the vectors of weights derived from FAMD and MCA contributions of each variable to the retained dimensions, and $\text{Size}_i$ represents the firm size control variable with its respective weights $d$, $e$, and $f$.


# 7. Results I

```{r yearTrendSize, echo=FALSE}
#### 3.1. SIZE_Rev Yearly lineplots by size by revenue ####

load(here("Data", "Processed", "CI_DD_comb_rev_weightedS11.rda")) ### Presented in Urbino

ci_dd_combined_rev <- ci_dd_combined_weighted

#### 0.1. Adding the quadrant varaible ####
# Add a new column for quadrants
combined_data_harmonized <- ci_dd_combined_rev %>%
  mutate(
    quadrant = case_when(
      access_n > 0.5 & secDD_n > 0.5 ~ "Q1 (H_A, H_S&U) )",
      access_n <= 0.5 & secDD_n > 0.5 ~ "Q2 (L_A, H_S&U)",
      access_n <= 0.5 & secDD_n <= 0.5 ~ "Q3 (L_A, L_S&U)",
      access_n > 0.5 & secDD_n <= 0.5 ~ "Q4 (H_A, L_S&U)"
    )
  )


combined_data_harmonized$year <- as.numeric(as.character(combined_data_harmonized$year))
# combined_data_harmonized$mac_sec <- as.factor(combined_data_harmonized$mac_sec)
combined_data_harmonized$quadrant <- as.factor(combined_data_harmonized$quadrant)




# Generate a line plot with access_n and skills_n
line_plot_by_size <- yearly_stats_and_plot(combined_data_harmonized, 
                                           line_vars = c("access_n", "skills_n", "usage_n"), 
                                           group_var = "size_rev", 
                                           statistic = "median")

line_plot_by_size

```


# 7.1. Results II

```{r yearTrendMac, echo=FALSE}
#### 3.3. MAC_SEC Yearly lineplots by size by revenue ####

# Generate a line plot with access_n and skills_n
line_plot_by_mac <- yearly_stats_and_plot(combined_data_harmonized, 
                                          line_vars = c("access_n", "skills_n", "usage_n"), 
                                          group_var = "mac_sec", 
                                          statistic = "median")

line_plot_by_mac
```



# 7.2. Results III

```{r yearTrendReg, echo=FALSE}

#### 3.5. REGION Yearly lineplots by size by revenue ####

# Generate a line plot with access_n and skills_n
line_plot_by_region <- yearly_stats_and_plot(combined_data_harmonized, 
                                             line_vars = c("access_n", "skills_n", "usage_n"), 
                                             group_var = "region", 
                                             statistic = "median")

line_plot_by_region
```



# 8. Q&A

Thank you for your attention

# References {.allowframebreaks}

::: {#refs}
:::
