---
title: 'Tracking the Digital Divide: Factor Analysis and Time Trends in Italian Firms'
author: "Luis Carlos Castillo"
date: "`r format(Sys.Date(), '%d %B %Y')`"
output:
  beamer_presentation:
    keep_tex: yes
    citation_package: natbib
    includes:
      in_header: mystyle3.tex
institute: |
  | Binational Doctorate
  | University of Urbino and Universty of Bremen
  | Ph.D. Program in Global Studies
  | Supervisor: Prof. Francesco Vidoli
  | Co-Supervisor: Prof. Dr. Christian Cordes
editor_options:
  markdown:
    wrap: 72
link-citations: yes
linkcolor: myblue
natbiboptions: round
header-includes:
 - \usepackage{etoolbox}
 - \AtBeginEnvironment{thebibliography}{\scriptsize}
bibliography: ShiftPatterns.bib
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = F, message = F )
kableExtra.auto_format = FALSE
knitr.table.format = "latex"
knitr::opts_knit$set(kable.force.latex = TRUE)



```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r Loading packages, include=FALSE}
library(tidyverse)
library(devtools)
library(here)
library(bibliometrix)
library(stringr)
library(readr)
library(visdat)
library(stringr)
library(dplyr)
library(readxl)
library(janitor)
library(ggplot2)
library(gridExtra)
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
library(rmarkdown)
library(tidytext)
library(knitr)
library(qwraps2)
library(dplyr)
library(tables)
library(bibtex)
library(igraph)
library(RColorBrewer)
library(Matrix)
library(flextable)
library(ggpubr)
library(cowplot)
library(ggeasy)
library(Hmisc)
library(gridGraphics)
library(gridBase)
library(tinytex)
library(stargazer)

source(here("Scripts", "Functions", "create_summary_table.R"))
source(here("Scripts", "Functions", "yearly_stats_and_plot.R"))

## Scheme 11: year,  region, Revenue_K,  sec_name, size_rev

```

# Cumulative Dissertation

```{=tex}
\begin{center}
\includegraphics[width=1.1\textwidth, height=1.2\textheight]{structure_thesis1.png}
\end{center}
```



# 1. Introduction

-   DT play a pivotal role in reshaping business models [@trischler2023]
    , driving innovation [@ciarli2021], and fostering competitive
    advantages [@jeganjosephjerome2024].

-   The unequal adoption of DT has led to significant challenge: the
    digital divide.

-   The digital divide at the firm level is a multifaceted gap
    characterized not only by disparities in access, skills and usage of
    DT, but also the derived benefits from different types of use.

-   While the digital divide is a global issue, its impact on
    enterprises, especially in Italy, presents unique challenges and
    opportunities.


# 2. Objectives

- Explore changes over time in the digital divide, focusing on differences across firm sizes, sectors, and regions.

-   Develop composite indices to track trends in the first and
    second-level digital divide.

-   Evaluate the alignment of resources and technology integration
    theory with observed data.

-   Propose targeted policy interventions based on research findings.


# 3. Data

```{r avgYear, echo=FALSE}

load(here("Data", "Processed", "CI_clean.rda"))

# Calculate the number of observations per year
options(scipen=999)
observations_per_year <- CI_clean %>%
  group_by(year) %>%
  summarise(count = n())

avgPerYear <- round(mean(observations_per_year$count),2)

```

-   The dataset was derived from the ICT Usage in Enterprises Survey
    conducted annually between 2014 and 2019 by ISTAT.
    
-   In total, 29 variables were used to extract three factors that represent the theoretical constructs.

    - Access index: 6 variables
    - Skills index: 9 variables
    - Usage index: 11 variables
    - **Control variable:** Firm size with three categories (small, medium, large)

-   Considerations and Limitations.

    -   Independence of Annual Data
    
-    Data treatments, codes, and summary statistics,  are available on my [GitHub repository](https://github.com/luchocastillo84/Factor_Analysis_Digital_Divide/tree/main) for replicability and further analysis.


# 4. Methodology

-   The indices were constructed using dimensionality reduction
    techniques Factor Analysis for Mixed Data (FAMD) and Multiple
    Correspondence Analysis (MCA).

$$ \text{Access Index}_i = \sum_{j=1}^{6} a_j \cdot X_{j,i} \cdot w_i $$
$$ \text{Skills Index}_i = \sum_{k=1}^{9} b_k \cdot Y_{k,i} \cdot w_i $$
$$ \text{Usage Index}_i = \sum_{m=1}^{11} c_m \cdot Z_{m,i} \cdot w_i $$

Where $\mathbf{X}$, $\mathbf{Y}$, and $\mathbf{Z}$ are the matrices of observations, $\mathbf{a}$, $\mathbf{b}$, and $\mathbf{c}$ are the vectors of weights derived from FAMD and MCA contributions of each variable to the retained dimensions, and $\mathbf{w}$ is the vector of weights accounting for the share of groups and years.



$$ \text{Access Index}_i = \sum_{j=1}^{6} a_j \cdot X_{j,i} $$
$$ \text{Skills Index}_i = \sum_{k=1}^{9} b_k \cdot Y_{k,i} $$
$$ \text{Usage Index}_i = \sum_{m=1}^{11} c_m \cdot Z_{m,i} $$



# 5. Results I

```{r yearTrendSize, echo=FALSE}
#### 3.1. SIZE_Rev Yearly lineplots by size by revenue ####

load(here("Data", "Processed", "CI_DD_comb_rev_weightedS11.rda")) ### Presented in Urbino

ci_dd_combined_rev <- ci_dd_combined_weighted

#### 0.1. Adding the quadrant varaible ####
# Add a new column for quadrants
combined_data_harmonized <- ci_dd_combined_rev %>%
  mutate(
    quadrant = case_when(
      access_n > 0.5 & secDD_n > 0.5 ~ "Q1 (H_A, H_S&U) )",
      access_n <= 0.5 & secDD_n > 0.5 ~ "Q2 (L_A, H_S&U)",
      access_n <= 0.5 & secDD_n <= 0.5 ~ "Q3 (L_A, L_S&U)",
      access_n > 0.5 & secDD_n <= 0.5 ~ "Q4 (H_A, L_S&U)"
    )
  )


combined_data_harmonized$year <- as.numeric(as.character(combined_data_harmonized$year))
# combined_data_harmonized$mac_sec <- as.factor(combined_data_harmonized$mac_sec)
combined_data_harmonized$quadrant <- as.factor(combined_data_harmonized$quadrant)




#### 3.2. SMEs_Rev Yearly lineplots by size by revenue ####

# Generate a line plot with access_n and skills_n
line_plot_by_smeR <- yearly_stats_and_plot(combined_data_harmonized, 
                                           line_vars = c("access_n", "skills_n", "usage_n"), 
                                           group_var = "sme_rev", 
                                           statistic = "median",
                                           size = "big",
                                           angle = F)
line_plot_by_smeR

```

#  Key takeaways I


- While SMEs can maintain continuous growth in access, larger firms face different challenges.

- These findings align with Bratta et al. (2020), who discuss the hyper-depreciation measure issued in 2016.

- SMEs face more challenges in acquiring digital skills. There is a significant shortage of ICT graduates in Italy according to the “Digital Skills Observatory” in 2019.

- A higher usage index is present in SMEs as existing technologies need to be operated either by outsourcing digital skills or maximising the existing workforce.


# 5.1. Results II

```{r yearTrendMac, echo=FALSE}
#### 3.3. MAC_SEC Yearly lineplots by size by revenue ####

# Generate a line plot with access_n and skills_n
line_plot_by_mac <- yearly_stats_and_plot(combined_data_harmonized, 
                                          line_vars = c("access_n", "skills_n", "usage_n"), 
                                          group_var = "mac_sec", 
                                          statistic = "median")

line_plot_by_mac
```

# Key takeaways II

- Notable progress in digital access across sectors due to effective policy measures like hyper-depreciation.

- The digital skills index remains low, highlighting challenges in developing necessary competencies.

- Commercial, Industrial, Service Sectors: Growing digital access and stable usage, but significant skills gap.

- Creative Industries and ICT Sector: High levels of access and skills but moderate usage, reflecting different technological needs in workflows.



# 5.2. Results III

```{r yearTrendReg, echo=FALSE}

#### 3.5. REGION Yearly lineplots by size by revenue ####

# Generate a line plot with access_n and skills_n

# Reordering factor levels using forcats::fct_relevel
combined_data_harmonized$region <- fct_relevel(combined_data_harmonized$region, 
                                               "Northwest", "Northeast", "Central", "South", "Insular")

line_plot_by_region <- yearly_stats_and_plot(combined_data_harmonized, 
                                             line_vars = c("access_n", "skills_n", "usage_n"), 
                                             group_var = "region", 
                                             statistic = "median")



line_plot_by_region
```

# Key takeaways III

- Northern and Central Regions:

    - Significant improvements in digital access.
    - Benefits from robust industrial bases and policy interventions.
    - Persistent skills gap, slight increase towards the end.
    
- South and Insular Regions:

    - Lag behind in both access and skills. Reflecting systemic issues.
    - Need targeted policy efforts.
    
- Usage Trends:

    - Similar trends across regions.
    - DT integration driven by national policies, market forces, and sectoral requirements.



# 6. Q&A

Thank you for your attention

# References {.allowframebreaks}

::: {#refs}
:::
