---
title: "Summary Statistics Regional Level"
author: "Luis Carlos Castillo"
date: "`r Sys.Date()`"
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
output:
  beamer_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
#### 0. Load the necessary packages #####
library(readr)
library(readxl)
library(dplyr)
library(tidyr)
library(here)
library(git2r)
library(visdat)
library(naniar)
library(chatgpt)
library(gptstudio)
require(devtools)
library(caret)
library(mice)
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE, warning = F, message = F )
kableExtra.auto_format = FALSE
knitr.table.format = "latex"
knitr::opts_knit$set(kable.force.latex = TRUE)

```


```{r loading_data, echo = FALSE}

load(here("Data", "Processed", "ICT_Combined.rda"))

counts_region_by_year <- ict_combined %>%
  dplyr::group_by(year, region) %>%
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  dplyr::group_by(year) %>%
  dplyr::mutate(total = sum(count),
                props = round(count / total * 100, 2)) 
```




## Why do we aggregate into macro sectors?

- **Enhanced Analytical Efficiency:** Aggregation simplifies data, enabling quicker and easier macroeconomic analysis, crucial for strategic decision-making.
- **Improved Comparative Analysis:** Macro sectors reduce variability, facilitating easier comparisons and benchmarking across economic dimensions, which enhances policy and investment strategies.
- **Streamlined Resource Allocation:** Aggregating sectors provides a clear overview of economic performance, aiding in more informed and effective resource distribution.
- **Simplified Communication:** The consolidation into macro sectors simplifies economic data presentation, making it more accessible and easier to understand for a wider audience.

## Limitations of aggregating sectors

- **Loss of Detailed Insights:** Aggregation may overlook critical sector-specific details and variations, potentially leading to less informed decisions.
- **Risk of Overgeneralization:** Broad categories can obscure the unique characteristics and needs of different industries, possibly resulting in unsuitable policies or strategies.
- **Masking of Intra-sector Disparities:** Aggregation can hide performance differences within sectors, potentially leading to misinformed assessments of economic health.
- **Impact on Statistical and Analytical Methods:** Could affect the robustness of statistical analyses. Significant variations within macro sectors can lead to misleading averages or other statistical measures.

## Macro Sector Mapping



## Count of Firms by Macro Sector by year

```{r mac_sectors_by_year, echo=FALSE}

# # Joining sector names to the original data
# ict_combined_mac <- left_join(ict_combined, sectors, by = "ateco_1")


# Summarize the data to count companies per sector and year
ict_summary <- ict_combined %>%
  group_by(region, year) %>%
  summarise(count = n(), .groups = 'drop')


# Pivot the data to wide format
ict_wide_mac <- ict_summary %>%
  pivot_wider(
    names_from = year,              # Define new column names from 'year'
    values_from = count,            # Fill the new columns with values from 'count'
    values_fill = list(count = 0))   # Fill missing values with 0

kable(ict_wide_mac, booktabs = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,5)

```


## Percentage of Firms by Macro Sectors by Year

```{r sec_props, echo=FALSE}


# Calculate total companies per year for normalization
year_totals_mac <- ict_combined %>%
  group_by(year) %>%
  summarise(total_count = n(), .groups = 'drop')

# Join the totals back to the summary data
ict_summary_mac <- left_join(ict_summary, year_totals_mac, by = "year")


# Calculate proportions
ict_summary_mac <- ict_summary_mac %>%
  mutate(proportion = round(count / total_count * 100,2))


ict_summary_mac1 <- ict_summary_mac %>%
  mutate(proportion = round(count / total_count * 100,2)) %>%
  dplyr::select(region, year, proportion)  # Select only the columns needed for pivoting

ict_wide_mac_prop <- ict_summary_mac1 %>%
  pivot_wider(
    names_from = year,              # Define new column names from 'year'
    values_from = proportion,       # Fill the new columns with values from 'proportion'
    values_fill = list(proportion = 0))  # Fill missing values with 0


# Use kable to format the wide table for LaTeX
kable(ict_wide_mac_prop, booktabs = TRUE) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%
  pack_rows("", 1, 5)

```





## Counts of Firms by Macro Sectors by Size 


```{r size, echo=FALSE}
# Count the observations of each level of CLAD4 grouped by year

# Recode and count observations, then calculate proportions

counts_size_by_mac <- ict_combined %>%
  dplyr::group_by(year, region, sme_rev) %>%
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  dplyr::group_by(year) %>%
  dplyr::mutate(total = sum(count),
                props = round(count / total, 3)) 

ict_wide_mac_count <- counts_size_by_mac %>%
  pivot_wider(
    id_cols = c(region, sme_rev),  # Keep 'macro_sector' and 'size' as row identifiers
    names_from = year,                # Create new column names from 'year'
    values_from = count,              # Fill the new columns with values from 'count'
    values_fill = list(count = 0)     # Fill missing values with 0 if there's no count for a given year
  )

kable(ict_wide_mac_count, booktabs = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,2) %>%   
  pack_rows("",3,4) %>%   
  pack_rows("",5,6) %>%   
  pack_rows("",7,8)%>%   
  pack_rows("",9,10)

```


## Percentage of Firms by Macro Sectors by Year

```{r sec_props_by_size, echo=FALSE}


ict_summary_mac1 <- counts_size_by_mac %>%
  dplyr::mutate(props = round(count / total * 100,2)) %>%
  dplyr::select(region, sme_rev, year, props)  # Select only the columns needed for pivoting

ict_wide_mac_prop <- ict_summary_mac1 %>%
  pivot_wider(
    names_from = year,              # Define new column names from 'year'
    values_from = props,       # Fill the new columns with values from 'proportion'
    values_fill = list(props = 0))  # Fill missing values with 0


# Use kable to format the wide table for LaTeX
kable(ict_wide_mac_prop, booktabs = TRUE) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,2) %>%   
  pack_rows("",3,4) %>%   
  pack_rows("",5,6) %>%   
  pack_rows("",7,8) %>%   
  pack_rows("",9,10)

```


