---
title: "Summary Statistics of 29 Variables by Firm"
author: "Luis Carlos Castillo"
date: "`r Sys.Date()`"
institute: |
  | 
  | University of Urbino and Universty of Bremen
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
output:
  beamer_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
#### 0. Load the necessary packages #####
library(readr)
library(readxl)
library(dplyr)
library(tidyr)
library(here)
library(git2r)
library(visdat)
library(naniar)
library(chatgpt)
library(gptstudio)
require(devtools)
library(caret)
library(mice)
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F )
kableExtra.auto_format = FALSE
knitr.table.format = "latex"
knitr::opts_knit$set(kable.force.latex = TRUE)

```


```{r loading_data, echo = FALSE}

load(here("Data", "Processed", "ICT_Combined.rda"))

ict_combined$A2_A2 <- ict_combined$A2_A2/ 100
ict_combined$A2_C2 <- ict_combined$A2_C2/ 100
ict_combined$A2_C6 <- ict_combined$A2_C6/ 100

```

## Introduction

This report details the active variables used for factor extraction. Variables with variance below 0.10 were excluded, as they do not contribute meaningful information to the results. This selection criterion ensures that the included variables provide significant insights into the underlying data structure and the constructs they represent (Access, Skills, and Usage).


## Firms Size Using 3 Levels Measured by Revenue

```{r size, echo=FALSE}
# Count the observations of each level of CLAD4 grouped by year

# Recode and count observations, then calculate proportions

library(dplyr)

counts_clad4_by_year <- ict_combined %>%
  group_by(year, size_rev) %>%
  summarise(count = n(), .groups = 'drop') %>%
  group_by(year) %>%
  mutate(total = sum(count),
         props = round(count / total, 3),
         variance = props * (1 - props)) # Add the variance calculation


kable(counts_clad4_by_year, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   pack_rows("",1,3) %>% pack_rows("",4,6) %>% pack_rows("",7,9) %>% pack_rows("",10,12) %>% pack_rows("",13,15) %>% pack_rows("",16,18)



```



## Firms Size Using 2 Levels Measured by Revenue

```{r size2, echo=FALSE}
# Count the observations of each level of CLAD4 grouped by year

# Recode and count observations, then calculate proportions

counts_clad4_by_year1 <- ict_combined %>%
  dplyr::group_by(year, sme_rev) %>%
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  dplyr::group_by(year) %>%
  dplyr::mutate(total = sum(count),
                props = round(count / total, 3)) 

kable(counts_clad4_by_year1, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   pack_rows("",1,2) %>% pack_rows("",3,4) %>% pack_rows("",5,6) %>% pack_rows("",7,8) %>% pack_rows("",9,10) %>% pack_rows("",11,12)

```

## Control Variables Used for Factor Extraction

In this study, firm size using 3 levels, measured by revenue, was included as an active variable in the factor analysis to control for its influence on other variables. This approach ensures that the extracted factors account for size-related variations, enhancing their interpretability and providing a comprehensive understanding of the data. Incorporating firm size allows for a more accurate and representative analysis of the underlying data structure.

## Revenue variable for firm size classification


The table below, based on ISTAT survey's documentation, outlines the revenue thresholds used for classifying firms by annual turnover. This classification is crucial for analyzing digital technology adoption across different enterprise sizes, ensuring a standardized approach according to European Commission guidelines.


```{r sizeRevenue, echo=FALSE}

options(scipen = 999)

thresholds <- data.frame(
  Revenue_label = c(0, 20000, 50000, 100000, 200000, 500000, 1000000, 2000000, 4000000, 5000000, 10000000, 20000000, 50000000, 200000000),
  Threshold = c("[0, 20000)", "[20000, 50000)", "[50000, 100000)", "[100000, 200000)", "[200000, 500000)", "[500000, 1000000)", 
                  "[1000000, 2000000)", "[2000000, 4000000)", "[4000000, 5000000)", "[5000000, 10000000)", "[10000000, 20000000)", 
                  "[20000000, 50000000)", "[50000000, 200000000)", "[200000000, + inf)")
)

kable(thresholds, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 5, latex_options = c("repeat_header")) %>%   pack_rows("",1,14)


```

## Firm size classification


The revenue variable is categorized into 11 thresholds. Firms are classified based on the Commission Recommendation of 6 May 2003:

1. **Small Enterprises**: Annual turnover not exceeding EUR 10 million.
2. **Medium Enterprises**: Annual turnover not exceeding EUR 50 million.
3. **Large Enterprises**: Annual turnover exceeding EUR 50 million.

These thresholds, as defined by the European Commission, ensure standardized firm size classification.



## Variables 

In total there are 29 variables use to extract the factors that represent each construct access, skills, and usage. Three control variables representing the firm size were included.

 - For the access index 6 variables + 3 size variables (small, medium, large)
 - For the skills index 9 variables + 3 size variables (small, medium, large)
 - For the usage index 11 variables + 3 size variables (small, medium, large)


## Variable Naming Conventions

The variables in this study are categorized to reflect different aspects of digital technology adoption:

- **A (Access)**: Includes 'A1' for incentives and 'A2' for physical access.
- **S (Skills)**: Measures digital skills within the enterprise, from ICT training and maintenance to advanced IT management.
- **U (Usage)**: Assesses the use of digital technologies in various operations:
  - **UM**: Management, including using ERP and CRM and human resources managemenet.
  - **UMK**: Marketing, focusing on digital marketing and sales.
  - **UC**: Commerce, tracking e-commerce and online transactions.

These conventions ensure clear identification and logical grouping of variables, facilitating streamlined analysis and interpretation.




## ACCESS Variables I


The 'ACCESS' category includes six variables, split into continuous and binary types, organized into two subcategories that highlight different facets of digital access:

1. **Incentives for Access (A1)**:
   - This includes a single variable, "IT training courses for employees without specialist ICT skills," aimed at fostering digital adoption by equipping employees with necessary skills.

2. **Physical Access (A2)**:
   - With five variables, this group measures physical aspects of digital access like computer availability and internet connectivity, critical for operational effectiveness and digital engagement in a competitive market.



## ACCESS variables II (Incentives)

-   Var name: IT training courses for employees without specialist ICT skills.
-   Type: binary
-   Code: A1\_B2b

```{r A1_B2b, echo=FALSE}

library(dplyr)

get_binary_summary_stats_by_group <- function(df, group_var, summary_var) {
  # Ensure the binary variable is treated as numeric
  df[[summary_var]] <- as.numeric(as.character(df[[summary_var]]))
  
  df %>%
    group_by(.data[[group_var]]) %>%
    summarise(
      count = n(),
      prop_1s = round(mean(.data[[summary_var]], na.rm = TRUE), 4),
      variance = round(prop_1s * (1 - prop_1s), 4), # Variance for binary variables
      std_dev = round(sd(.data[[summary_var]], na.rm = TRUE), 4),
      .groups = 'drop'
    ) %>%
    mutate(
      lo_95_CI = round(prop_1s - 1.96 * sqrt(prop_1s * (1 - prop_1s) / count), 2),
      up_95_CI = round(prop_1s + 1.96 * sqrt(prop_1s * (1 - prop_1s) / count), 2)
    )
}


# Example usage:
A1_B2b_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "A1_B2b")

# Make sure to use the format "latex" for PDF output


kable(A1_B2b_summary, "latex", longtable = F, booktabs = T,escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)




```


## ACCESS variables III (Physical Access)

-   Var name: Percentage of employees using the computer out of the total employees.
-   Type: continuous
-   Code: A2\_A2

```{r A2_A2, echo= F}



get_summary_continuous_stats_by_group <- function(df, group_var, summary_var) {
  df %>%
    group_by({{ group_var }}) %>%
    summarise(
      count = n(),
      mean = round(mean({{ summary_var }}, na.rm = TRUE), 4),
      sd = round(sd({{ summary_var }}, na.rm = TRUE), 4),
      variance = round(var({{ summary_var }}, na.rm = TRUE), 4), # Added variance calculation
      median = round(median({{ summary_var }}, na.rm = TRUE), 2),
      min = round(min({{ summary_var }}, na.rm = TRUE), 2),
      max = round(max({{ summary_var }}, na.rm = TRUE), 2),
      IQR = round(IQR({{ summary_var }}, na.rm = TRUE), 2)
    )
}

A2_A2_summary <- get_summary_continuous_stats_by_group(ict_combined, year, A2_A2)


kable(A2_A2_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)


```

## ACCESS variables IV (Physical Access)

Density plot

```{r density_plot_A2_A2, echo= F}

# Plot density for access_n by year
ggplot(ict_combined, aes(x = A2_A2, fill = year)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~ year) +
  labs(title = "Density Plot for A2_A2 by Year",
       x = "A2_A2",
       y = "Density") +
  scale_fill_brewer(palette = "Set1")
```


## ACCESS variables V (Physical Access)

-   Var name: Percentage of employees using computers connected to the internet.
-   Type: continuous
-   Code: A2\_C2

```{r A2_C2, echo= F}

A2_C2_summary <- get_summary_continuous_stats_by_group(ict_combined, year, A2_C2)


kable(A2_C2_summary, "latex", longtable = F, booktabs = T , escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)


```

## ACCESS variables VI (Physical Access)

Density plot

```{r density_plot_A2_C2, echo= F}

# Plot density for access_n by year
ggplot(ict_combined, aes(x = A2_C2, fill = year)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~ year) +
  labs(title = "Density Plot for A2_C2 by Year",
       x = "A2_C2",
       y = "Density") +
  scale_fill_brewer(palette = "Set1")
```


## ACCESS variables VII (Physical Access)

-   Var name: Enterprise provides mobile devices with mobile connection.
-   Type: binary
-   Code: A2\_C5a

```{r A2_C5a, echo= F}

A2_C5a_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "A2_C5a")


kable(A2_C5a_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)


```


## ACCESS variables VIII (Physical Access)

-   Internet download speed low between 2 Mbit/s to 30 Mbit/s.
-   Type: continuous
-   Code: A2\_C4\_low

```{r A2_C4_low, echo= F}

A2_C4_low_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "A2_C4_low")


kable(A2_C4_low_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)


```


## ACCESS variables IX (Physical Access)

-   Internet download speed low between 2 Mbit/s to 30 Mbit/s.
-   Type: continuous
-   Code: A2\_C4\_high

```{r A2_C4_high, echo= F}

A2_C4_high_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "A2_C4_high")


kable(A2_C4_high_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)


```




## SKILLS variables I


This category encompasses nine binary variables identified by the prefix "S", which measure the presence and utilization of internal personnel for ICT tasks within enterprises. These variables span a range of functions from infrastructure maintenance to web development and IT security management, reflecting the enterprise's depth of digital skills and training in key ICT domains.




## SKILLS variables II 

-   Var name: Employment of specialists in computer subjects.
-   Type: binary
-   Code: S_B1

```{r S_B1, echo=FALSE}

# Example usage:
S_B1_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "S_B1")

# Make sure to use the format "latex" for PDF output


kable(S_B1_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```



## SKILLS variables III

-   Var name: IT training courses for employees with specialist ict skills.
-   Type: binary
-   Code: S_B2a

```{r S_B2a, echo=FALSE}

# Example usage:
S_B2a_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "S_B2a")

# Make sure to use the format "latex" for PDF output


kable(S_B2a_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```



## SKILLS variables IV

-   Use of internal personnel for ICT infrastructure maintenance.
-   Type: binary
-   Code: S_B5a1

```{r S_B5a1, echo=FALSE}

# Example usage:
S_B5a1_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "S_B5a1")

# Make sure to use the format "latex" for PDF output


kable(S_B5a1_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%
  pack_rows("",1,6)
```

## SKILLS variables V

-   Var name: Use of internal personnel for office software support.
-   Type: binary
-   Code: S_B5b1

```{r S_B5b1, echo=FALSE}

# Example usage:
S_B5b1_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "S_B5b1")

# Make sure to use the format "latex" for PDF output


kable(S_B5b1_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%
  pack_rows("",1,6)
```


## SKILLS variables VI

-   Var name: Use of internal personnel for enterprise software development.
-   Type: binary
-   Code: S_B5c1

```{r S_B5c1, echo=FALSE}

# Example usage:
S_B5c1_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "S_B5c1")

# Make sure to use the format "latex" for PDF output


kable(S_B5c1_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%
  pack_rows("",1,6)
```


## SKILLS variables VII

-   Var name: Use of internal personnel for enterprise software support.
-   Type: binary
-   Code: S_B5d1

```{r S_B5d1, echo=FALSE}

# Example usage:
S_B5d1_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "S_B5d1")

# Make sure to use the format "latex" for PDF output


kable(S_B5d1_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%
  pack_rows("",1,6)
```


## SKILLS variables VIII

-   Var name: Use of internal personnel for enterprise software support.
-   Type: binary
-   Code: S_B5e1

```{r S_B5e1, echo=FALSE}

# Example usage:
S_B5e1_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "S_B5e1")

# Make sure to use the format "latex" for PDF output


kable(S_B5e1_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%
  pack_rows("",1,6)
```

## SKILLS variables IX

-   Var name: Use of internal personnel for web development support.
-   Type: binary
-   Code: S_B5f1

```{r S_B5f1, echo=FALSE}

# Example usage:
S_B5f1_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "S_B5f1")

# Make sure to use the format "latex" for PDF output


kable(S_B5f1_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%
  pack_rows("",1,6)
```


## SKILLS variables X

-   Var name: Use of internal personnel for web development support.
-   Type: binary
-   Code: S_B5g1

```{r S_B5g1, echo=FALSE}

# Example usage:
S_B5g1_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "S_B5g1")

# Make sure to use the format "latex" for PDF output


kable(S_B5g1_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%
  pack_rows("",1,6)
```



## USAGE variables I



This section details the usage category, which consists of 11 binary variables prefixed with "U", delineating how enterprises apply digital technologies across various functional domains. These variables are structured into distinct groups representing different business operations:

- **UM (Management)**: Variables under this prefix measure the integration of digital tools such as ERP and CRM in management processes and  human resources management.
- **UMK (Marketing)**: These variables assess digital applications in marketing activities.
- **UC (Commerce)**: This group captures the use of digital technologies in e-commerce operations.

This classification helps highlight the diverse applications of digital technologies and the specific business functions they enhance within the enterprise.



## USAGE variables II (Marketing)

-   Var name: Use of Website
-   Type: binary
-   Code: UMK_C7

```{r UMK_C7, echo=FALSE}

# Example usage:
UMK_C7_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "UMK_C7")

# Make sure to use the format "latex" for PDF output


kable(UMK_C7_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```



## USAGE variables III (Marketing)

-   Var name: possibility to place orders or reservations online eg online shopping cart
-   Type: binary
-   Code: UMK_C8c

```{r UMK_C8c, echo=FALSE}

# Example usage:
UMK_C8c_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "UMK_C8c")

# Make sure to use the format "latex" for PDF output


kable(UMK_C8c_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```



## USAGE variables IV (Marketing)

-   Var name: Links or references to company profiles on social media
-   Type: binary
-   Code: UMK_C8h

```{r UMK_C8h, echo=FALSE}

# Example usage:
UMK_C8h_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "UMK_C8h")

# Make sure to use the format "latex" for PDF output


kable(UMK_C8h_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```


## USAGE variables V (Marketing)

-   Var name: Use of social network.
-   Type: binary
-   Code: UMK_C10a

```{r UMK_C10a, echo=FALSE}

# Example usage:
UMK_C10a_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "UMK_C10a")

# Make sure to use the format "latex" for PDF output


kable(UMK_C10a_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```

## USAGE variables VI (Marketing)

-   Var name: Social media and multimedia.
-   Type: binary
-   Code: UMK_C10c

```{r UMK_C10c, echo=FALSE}

# Example usage:
UMK_C10c_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "UMK_C10c")

# Make sure to use the format "latex" for PDF output


kable(UMK_C10c_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```


## USAGE variables VII (Management)

-   Var name: Using ERP software
-   Type: binary
-   Code: UM_E1

```{r UM_E1, echo=FALSE}

# Example usage:
UM_E1_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "UM_E1")

# Make sure to use the format "latex" for PDF output


kable(UM_E1_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```


## USAGE variables VIII (Management)

-   Var name: Use operational CRM software
-   Type: binary
-   Code: UM_E2b

```{r UM_E2b, echo=FALSE}

# Example usage:
UM_E2b_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "UM_E2b")

# Make sure to use the format "latex" for PDF output


kable(UM_E2b_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```


## USAGE variables IX (Management)

-   Var name: Use analytical CRM software
-   Type: binary
-   Code: UM_E2a

```{r UM_E2a, echo=FALSE}

# Example usage:
UM_E2a_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "UM_E2a")

# Make sure to use the format "latex" for PDF output


kable(UM_E2a_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```

## USAGE variables XI (e-commerce)

-   Var name: Possibility to place orders or reservations online eg online shopping cart
-   Type: binary
-   Code: UC_C8a

```{r UC_C8a, echo=FALSE}

# Example usage:
UC_C8a_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "UC_C8a")

# Make sure to use the format "latex" for PDF output


kable(UC_C8a_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```


## USAGE variables XII (e-commerce)

-   Var name: Web sales through intermediary websites or ecommerce sites marketplaces or apps
-   Type: binary
-   Code: UC_J7

```{r UC_J7, echo=FALSE}

# Example usage:
UC_J7_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "UC_J7")

# Make sure to use the format "latex" for PDF output


kable(UC_J7_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```


## USAGE variables XIII (Human Resources)

-   Var name: Announcement of vacancies or possibility to apply for employment online.
-   Type: binary
-   Code: UM_C8g

```{r UM_C8g, echo=FALSE}

# Example usage:
UM_C8g_summary <- get_binary_summary_stats_by_group(ict_combined, "year", "UM_C8g")

# Make sure to use the format "latex" for PDF output


kable(UM_C8g_summary, "latex", longtable = F, booktabs = T, escape = T) %>%
  kable_styling(font_size = 6, latex_options = c("repeat_header")) %>%   
  pack_rows("",1,6)
```


